\chapter*{Bibliographie}
\addcontentsline{toc}{chapter}{Bibliographie}

\section*{Documentations Techniques}

\noindent [1] \textbf{Spring Framework Documentation}. \textit{Spring Boot Reference Guide}. Spring Team, 2024. \\
\url{https://docs.spring.io/spring-boot/docs/current/reference/html/}

\noindent [2] \textbf{Spring Security Documentation}. \textit{Spring Security Reference}. Spring Security Team, 2024. \\
\url{https://docs.spring.io/spring-security/reference/}

\noindent [3] \textbf{Spring Data JPA Documentation}. \textit{Spring Data JPA - Reference Documentation}. Spring Data Team, 2024. \\
\url{https://docs.spring.io/spring-data/jpa/docs/current/reference/html/}

\noindent [4] \textbf{Spring Data MongoDB Documentation}. \textit{Spring Data MongoDB - Reference Documentation}. Spring Data Team, 2024. \\
\url{https://docs.spring.io/spring-data/mongodb/docs/current/reference/html/}

\noindent [5] \textbf{React Documentation}. \textit{React - A JavaScript library for building user interfaces}. Meta Open Source, 2024. \\
\url{https://react.dev/}

\noindent [6] \textbf{MongoDB Documentation}. \textit{MongoDB Manual}. MongoDB Inc., 2024. \\
\url{https://docs.mongodb.com/manual/}

\noindent [7] \textbf{MySQL Documentation}. \textit{MySQL 8.0 Reference Manual}. Oracle Corporation, 2024. \\
\url{https://dev.mysql.com/doc/refman/8.0/en/}

\noindent [8] \textbf{Keycloak Documentation}. \textit{Keycloak Server Administration Guide}. Red Hat Inc., 2024. \\
\url{https://www.keycloak.org/documentation}

\noindent [9] \textbf{Leaflet Documentation}. \textit{Leaflet - An open-source JavaScript library for mobile-friendly interactive maps}. Vladimir Agafonkin, 2024. \\
\url{https://leafletjs.com/reference.html}

\noindent [10] \textbf{React Leaflet Documentation}. \textit{React components for Leaflet maps}. React Leaflet Team, 2024. \\
\url{https://react-leaflet.js.org/}

\section*{Standards et Spécifications}

\noindent [11] \textbf{OAuth 2.0 Authorization Framework}. D. Hardt, Ed. RFC 6749, IETF, October 2012. \\
\url{https://tools.ietf.org/html/rfc6749}

\noindent [12] \textbf{OpenID Connect Core 1.0}. N. Sakimura, J. Bradley, M. Jones, B. de Medeiros, C. Mortimore. OpenID Foundation, November 2014. \\
\url{https://openid.net/specs/openid-connect-core-1_0.html}

\noindent [13] \textbf{JSON Web Token (JWT)}. M. Jones, J. Bradley, N. Sakimura. RFC 7519, IETF, May 2015. \\
\url{https://tools.ietf.org/html/rfc7519}

\noindent [14] \textbf{REST API Design Guidelines}. Roy Fielding. \textit{Architectural Styles and the Design of Network-based Software Architectures}. University of California, Irvine, 2000.

\section*{Outils de Développement}

\noindent [15] \textbf{IntelliJ IDEA Documentation}. \textit{IntelliJ IDEA Help}. JetBrains s.r.o., 2024. \\
\url{https://www.jetbrains.com/help/idea/}

\noindent [16] \textbf{Visual Studio Code Documentation}. \textit{VS Code Docs}. Microsoft Corporation, 2024. \\
\url{https://code.visualstudio.com/docs}

\noindent [17] \textbf{Git Documentation}. \textit{Git Reference Manual}. Software Freedom Conservancy, 2024. \\
\url{https://git-scm.com/docs}

\noindent [18] \textbf{Docker Documentation}. \textit{Docker Official Documentation}. Docker Inc., 2024. \\
\url{https://docs.docker.com/}

\noindent [19] \textbf{Postman Documentation}. \textit{Postman Learning Center}. Postman Inc., 2024. \\
\url{https://learning.postman.com/docs/}

\noindent [20] \textbf{MongoDB Compass Documentation}. \textit{MongoDB Compass}. MongoDB Inc., 2024. \\
\url{https://docs.mongodb.com/compass/}

\section*{Bibliothèques et Frameworks Frontend}

\noindent [21] \textbf{Axios Documentation}. \textit{Promise based HTTP client for the browser and node.js}. Matt Zabriskie, 2024. \\
\url{https://axios-http.com/docs/intro}

\noindent [22] \textbf{React Router Documentation}. \textit{Declarative routing for React}. Remix Software Inc., 2024. \\
\url{https://reactrouter.com/}

\noindent [23] \textbf{Bootstrap Documentation}. \textit{Bootstrap - The most popular HTML, CSS, and JS library}. The Bootstrap Team, 2024. \\
\url{https://getbootstrap.com/docs/}

\noindent [24] \textbf{Leaflet.markercluster Documentation}. \textit{Provides Beautiful Animated Marker Clustering functionality for Leaflet}. Dave Leaver, 2024. \\
\url{https://github.com/Leaflet/Leaflet.markercluster}

\section*{Bases de Données et Performance}

\noindent [29] \textbf{Kristina Chodorow}. \textit{MongoDB: The Definitive Guide}. O'Reilly Media, 3rd Edition, 2019.

\noindent [30] \textbf{Baron Schwartz, Peter Zaitsev, Vadim Tkachenko}. \textit{High Performance MySQL}. O'Reilly Media, 4th Edition, 2021.

\noindent [31] \textbf{Rick Houlihan}. \textit{Amazon DynamoDB Deep Dive: Advanced Design Patterns}. AWS re:Invent, 2019.

\section*{Sécurité et Authentification}

\noindent [32] \textbf{Jan Stenberg}. \textit{Identity and Access Management with OAuth 2.0 and OpenID Connect}. InfoQ, 2022.

\noindent [33] \textbf{John Bradley, Nat Sakimura}. \textit{OAuth 2.0 and OpenID Connect Security Best Practices}. OAuth Working Group, 2021.

\noindent [34] \textbf{OWASP Foundation}. \textit{OWASP Top Ten Web Application Security Risks}. OWASP, 2021. \\
\url{https://owasp.org/www-project-top-ten/}

\section*{Développement et DevOps}

\noindent [35] \textbf{Jez Humble, David Farley}. \textit{Continuous Delivery: Reliable Software Releases through Build, Test, and Deployment Automation}. Addison-Wesley Professional, 2010.

\noindent [36] \textbf{Gene Kim, Patrick Debois, John Willis, Jez Humble}. \textit{The DevOps Handbook: How to Create World-Class Agility, Reliability, and Security in Technology Organizations}. IT Revolution Press, 2016.

\noindent [37] \textbf{GitHub Docs}. \textit{GitHub Projects Documentation}. GitHub Inc., 2024. \\
\url{https://docs.github.com/en/issues/planning-and-tracking-with-projects}

\section*{Ressources Web et Tutoriels}

\noindent [41] \textbf{Baeldung}. \textit{Spring Boot Tutorials}. Eugen Paraschiv, 2024. \\
\url{https://www.baeldung.com/spring-boot}

\noindent [42] \textbf{Spring Guides}. \textit{Getting Started with Spring Boot}. Spring Team, 2024. \\
\url{https://spring.io/guides}

\noindent [43] \textbf{React Official Tutorial}. \textit{Tutorial: Intro to React}. Meta Open Source, 2024. \\
\url{https://react.dev/learn/tutorial-tic-tac-toe}

\noindent [44] \textbf{MongoDB University}. \textit{MongoDB for Developers}. MongoDB Inc., 2024. \\
\url{https://university.mongodb.com/}

\noindent [45] \textbf{Keycloak Community}. \textit{Keycloak Blog and Tutorials}. Red Hat Inc., 2024. \\
\url{https://www.keycloak.org/guides}

